---
title: "MLWIC2_processing_occupancy"
author: "Brandon Mayer"
date: "5/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MLWIC2)
```


For starters, we'll examine how well the available empty_animal model can sort out false captures (False Positive "FP") or empty photos
*note: The absolute paths are used to locate the necessary files. 

- The`classify` function has 5 static parameters.
<br>
    - `path_prefix`  
        - This is the absolute path to the total resized images reside. In the Walkthrough markdown, we consolidated all of the photos to a single folder. 
        - Because we are examining whether the photo is empty or not, the number of individuals in each photo is unnecessary.
<br>       
    - `data_info`
        - This is the location of the .csv containing information about the images. 
        - In the Walkthrough Markdown we renamed and structured the .CSV the have no headers.
          - The first column contained the basename of each photo.
          - The second column includes a value for the photos since the same format is used in training. The walkthrough, autofills to 0 a value isnt included.
        - *This file should be named image_labels.csv and it should be located in the MLWIC_helper_files folder.* 
<br>
    - `model_dir`
        - This is where you stored the *MLWIC_helper_files* folder  .
<br>   
    - `python_loc`
        - The location of Python on your computer.
        - *Note: You MUST have a slash ("/") at the end of the path!!!**
```{r}
# add the path to Anaconda her as well. 
condapath <- ""
```
        
<br>
    - `os`
        - Default is set to "Mac". Change to 'Windows'if necessary.

- Additionally includes 3 changeable parameters.
<br>
    - `log_dir`
        - This allows the user to choose the model they with to use on their photos.
        - There are two base models available from the *MLWIC_helper_files* we downloaded in the previous markdown file. 

            1. empty_animal
            2. Species_animal
<br>
    - `output_name`
        - model_predictions.txt are automatically transformed into an easy to read .csv.
        - This defaults to *MLWIC2_output*, but can be adjusted so it isnt overwritten. 
 <br>
    - `num_classes`
        - This represents the number of available scores the machine will assign the the photo. 
        - Occupancy is binary so only two scores (0 and 1) are used. 
        - This will consist of the number of species in youre examining for when scoring for species. 

# Classifying
```{r}

### Example using absolute paths
# classify(
#   path_prefix = "C:/Users/brand/Documents/MLWIC/MLWIC_unmediated",
#   data_info = "C:/Users/brand/Documents/MLWIC/MLWIC_unmediated/MLWIC2_helper_files/image_labels.csv",
#   model_dir = "C:/Users/brand/Documents/MLWIC/MLWIC_unmediated/MLWIC2_helper_files",
#   python_loc = "C:/Users/brand/Anaconda3/", # remember to include the last slash
#   log_dir = "empty_animal",
#   save_predictions = "model_predictions2.txt", 
#   os = 'Windows',
#   num_classes = 2
#   )

classify(
 path_prefix = paste0(getwd(), "/images"), # absolute path to location of the images on your computer. Should be in the immediate directory
  data_info = paste0(getwd(), "/MLWIC2_helper_files/image_labels.csv"), #
  model_dir = paste0(getwd(), "/MLWIC2_helper_files"),
  python_loc = condapath,
  log_dir = "empty_animal",
  save_predictions = "model_predictions.txt", # raw form
  output_name = "MLWIC2_output.csv",
  os = 'Windows',
  num_classes = 2
)
  
```

# Testing for the empty_animal model for Recall 
## Deciding on on threshold is a balancing game between precision and recall. By increasing one we see a decrease in the other. For our sorting needs, we're interested in capturing all of the occupied photos so we're aiming to reduce False Negatives. This will result in a higher precision, but extra photos are a small cost for increased data. 

```{r}
output <- read.csv(paste(getwd(),"/MLWIC2_helper_files/MLWIC2_output.csv", sep =""))

# basic accuracy comparing correct answers to the results
correct_predictions <- output$answer==output$guess1
base_accuracy <- if (correct_predictions==TRUE){sum(correct_predictions)}/length(correct_predictions)

# binomial check
TP <- sum(output$answer == 1 & output$guess1 == 1)
TN <- sum(output$answer == 0 & output$guess1 == 0)
FP <- sum(output$answer == 1 & !output$guess1 == 1)
FN <- sum(output$answer == 0 & !output$guess1 == 0)

accuracy <- (TP+TN)/(TP+TN+FP+FN) 

# What proportion of positive identifications was actually correct?
Precision <- TP/(TP+FP)

# What proportion of actual positives was identified correctly?
Recall <- TP/ (TP+FN)

# in our case maxing out Precision is the best bet. Better to have all of the occupied photos and sort through extras than to miss out on occupied photos.
```

This will be the bread and butter of how you approach training. Training under new parameters, and testing the newly classified photos will help you maximize recall. 

# Training with your own results. 

The current settings are set to retrain the empty_animal model. This focuses on occupancy and only has 2 classes

*Note: The train function has extra parameters that allow you to select variious detail of how you want to train the new model. 

```{r}
train(  path_prefix = paste0(getwd(), "/images"), # absolute path to location of the images on your computer
  data_info = paste0(getwd(), "/MLWIC2_helper_files/image_labels.csv"), # csv with file names for each photo. See details
  model_dir = paste0(getwd(), "/MLWIC2_helper_files"),
  python_loc = condapath,
  os="Windows",
  num_gpus = 2,
  num_classes = 2, # number of classes in model
  delimiter = ",", # this will be , for a csv.
  architecture = "resnet",
  depth = "18",
  batch_size = 128,
  log_dir = "Your_unique_model",
  log_dir_train = "MLWIC2_train_output",
  retrain = TRUE,
  retrain_from = "empty_animal",
  num_epochs = 5, # Number of rounds of
  randomize = TRUE,
  max_to_keep = 2,
  print_cmd = FALSE,
  shiny=FALSE
)
```

# Included here will be a step by step breakdown of how to approach fine-tuning the model. 

# A Third script will follow tackling species identification. 

